Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-10-05 paper-kelompok/main.tex
delete comments
figure scaling
connect citing

% \title{Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System}

% \author{\IEEEauthorblockN{Alzana Armaniar Farhani}
% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
% \textit{Institut Teknologi Bandung}\\
% Bandung, Indonesia\\
% Email: farhanialzana@gmail.com}
% \and
% \IEEEauthorblockN{Balkan Khilmi Assakandari}
% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
% \textit{Institut Teknologi Bandung}\\
% Bandung, Indonesia\\
% Email: balkankhilmi@gmail.com}
% \and
% \IEEEauthorblockN{Anindhita Nayazirly}
% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
% \textit{Institut Teknologi Bandung}\\
% Bandung, Indonesia\\
% Email: zirlysukarno@gmail.com}
% \and
% \IEEEauthorblockN{Akhmadi Surawijaya}
% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
% \textit{Institut Teknologi Bandung}\\
% Bandung, Indonesia\\
% Email: }
% \and
% \IEEEauthorblockN{Muhammad Ogin Hasanuddin}
% \IEEEauthorblockA{\textit{School of Electrical Engineering and Informatics}\\
% \textit{Institut Teknologi Bandung}\\
% Bandung, Indonesia\\
% Email: }}

% % ini komentar
% \maketitle

@@

Meanwhile, for quantitative analysis, the absorbance level of the sample for a specific wavelength is directly proportional to the concentration of the sample. Glucose spectrophotometry test includes colorimetric measurement methods, namely measurements that involve changing the color of the sample to measure quantities such as absorbance and sample concentration. Various colorimetric methods involving reactions with different enzymes for glucose measurement are the object of research being developed to obtain colorimetric methods that are accurate, sensitive, selective, and inexpensive.  Several approaches were studied to develop a colorimetric glucose biosensor by using glucose oxidase (GOx) to oxidize glucose to gluconic acid and hydrogen peroxide (H2O2). In colorimetric assays, studies revealed that the Horseradish Peroxidase (HRP) enzyme could catalyze the reaction of H2O2 and organic substrates such as 3,3',5,5'-tetramethylbenzidine (TMB) to produce visible colors[1].

Microfluidics offer several advantages for glucose analysis, such as reduced sample and reagent consumption, faster analysis, portability, and high compatibility with multiplexing detection means. One application called digital microfluidics (DMF) has a promising potential to operate microdroplets in portable analytical systems. The platform is based on the droplet manipulation using electrowetting-on-dielectric (EWOD) principle which applies electric potential to the control electrodes coated with a hydrophobic dielectric[2]. The DMF system mainly consists of a fluid layer located between the top and bottom plates. Nowadays, DMF technology is commonly used for various processes which include sample preparation and diagnostics[3]. Droplet mixing allows all chemical reactions to be done on chip. An optical detection system needs to be developed in order to measure the absorbance and concentration of a glucose droplet on the DMF chip.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics{system-dfd.png}}
    \caption{Level-1 Data Flow Diagram (DFD) of the system.}
    \label{system-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics{light-source-dfd.png}}
    \caption{DFD of the light source subsystem.}
    \label{light-source-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics{light-sensor-dfd.png}}
    \caption{DFD of the light sensor subsystem.}
    \label{light-sensor-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics{ui-dfd.png}}
    \caption{DFD of the user interface subsystem.}
    \label{ui-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics{power-dfd.png}}
    \caption{DFD of the power subsystem.}
    \label{power-dfd}
    \end{figure}

>>>>

@@

Meanwhile, for quantitative analysis, the absorbance level of the sample for a specific wavelength is directly proportional to the concentration of the sample. Glucose spectrophotometry test includes colorimetric measurement methods, namely measurements that involve changing the color of the sample to measure quantities such as absorbance and sample concentration. Various colorimetric methods involving reactions with different enzymes for glucose measurement are the object of research being developed to obtain colorimetric methods that are accurate, sensitive, selective, and inexpensive.  Several approaches were studied to develop a colorimetric glucose biosensor by using glucose oxidase (GOx) to oxidize glucose to gluconic acid and hydrogen peroxide (H2O2). In colorimetric assays, studies revealed that the Horseradish Peroxidase (HRP) enzyme could catalyze the reaction of H2O2 and organic substrates such as 3,3',5,5'-tetramethylbenzidine (TMB) to produce visible colors\cite{b1}.

Microfluidics offer several advantages for glucose analysis, such as reduced sample and reagent consumption, faster analysis, portability, and high compatibility with multiplexing detection means. One application called digital microfluidics (DMF) has a promising potential to operate microdroplets in portable analytical systems. The platform is based on the droplet manipulation using electrowetting-on-dielectric (EWOD) principle which applies electric potential to the control electrodes coated with a hydrophobic dielectric\cite{b2}. The DMF system mainly consists of a fluid layer located between the top and bottom plates. Nowadays, DMF technology is commonly used for various processes which include sample preparation and diagnostics\cite{b3}. Droplet mixing allows all chemical reactions to be done on chip. An optical detection system needs to be developed in order to measure the absorbance and concentration of a glucose droplet on the DMF chip.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.4]{system-dfd.png}}
    \caption{Level-1 Data Flow Diagram (DFD) of the system.}
    \label{system-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{light-source-dfd.png}}
    \caption{DFD of the light source subsystem.}
    \label{light-source-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.4]{light-sensor-dfd.png}}
    \caption{DFD of the light sensor subsystem.}
    \label{light-sensor-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.4]{ui-dfd.png}}
    \caption{DFD of the user interface subsystem.}
    \label{ui-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{power-dfd.png}}
    \caption{DFD of the power subsystem.}
    \label{power-dfd}
    \end{figure}
